Evolution of pre-copulatory and post-copulatory inbreeding behaviour and associated

### 2017-03-11 ms_pre_post.Rmd
Final edits before sending to coauthors

---
title: Evolution of pre-copulatory and post-copulatory inbreeding behaviour and associated
  polyandry
author: ''
date: "December 15, 2016"
output:
  html_document: default
  pdf_document:
    fig_caption: yes
  word_document:
    fig_caption: yes
    pandoc_args:
    - --csl
    - evolution.csl
    reference_docx: docx_template.docx
header-includes:
- \usepackage{natbib}
- \usepackage{lineno}
- \linenumbers
- \bibliographystyle{amnatnat}
linestretch: 2
csl: evolution.csl
bibliography: ms_pre_post.bib
---

@@

<!--- I think that the addition to the last sentence here is probably an improvement, but it still doesn't quite address my question -- there's not much of an argument for concluding that dynamic models are *required*. The implicit argument seems to be something like, ''look, there's a lot of complex stuff that's happening here; we can't figure out how to model how the evolutionary trajectories will play out without a dynamic model, so we're just going to assume that it's not possible''. My tendency is to be careful with these kinds of bold claims, and maybe instead emphasise that dynamic models *can be useful* for understanding these kinds of dynamics without suggesting that they are necessary (time will tell if this is true -- I don't want to dissuade someone from giving it a shot -- Corina tarnita, whose work I've often disagreed with, made a good point about this in a recent comment of Physics of Life Reviews). --->

@@

<!--- Last time we were through this, it was suggested that I scrap the former term ''inbreeding strategy'' because we don't deal at all with inbreeding preference. I have rewritten these sections in attempt to make the writing clearer. TODO: Additionally, I have tweaked the figure legends appropriately.--->

@@

Evolution of reproductive strategies cannot be presumed to occur in isolation in wild populations, and is instead likely to involve multiple interacting phenotypes resulting in the potential for feedback and degeneracy (i.e., functional redundance) among phenotypes under selection. For example, strong inbreeding depression in offspring fitness is widely hypothesised to drive selection for inbreeding avoidance, which could consequently feed back to drive selection for polyandry [e.g., @Zeh1997; @Jennions2000; @Tregenza2002]. Evolution of inbreeding avoidance can be driven by selection on both pre-copulatory and post-copulatory mechanisms, so simultaneous evolution of each phenotype is likely to be affected by degeneracy, in addition to any direct costs on phenotypes. We used individual-based modelling to explore evolution of pre-copulatory and post-copulatory inbreeding avoidance and polyandry given (1) hard constraints on evolution of post-copulatory inbreeding avoidance, (2) asymmetric costs of pre-copulatory and post-copulatory inbreeding avoidance, and (3) evolution of one inbreeding avoidance phenotype given the pre-existence the other. We thereby highlight fundamental but theoretically under-developed relationships between evolution of female mating frequency and pre-copulatory versus post-copulatory inbreeding avoidance.

>>>>

---
title: Evolution of pre-copulatory and post-copulatory inbreeding behaviour and associated
  polyandry
author: ''
date: "December 15, 2016"
output:
  pdf_document:
    fig_caption: yes
  html_document: default
  word_document:
    fig_caption: yes
    pandoc_args:
    - --csl
    - evolution.csl
    reference_docx: docx_template.docx
header-includes:
- \usepackage{natbib}
- \usepackage{lineno}
- \linenumbers
- \bibliographystyle{amnatnat}
linestretch: 2
csl: evolution.csl
bibliography: ms_pre_post.bib
---

@@

<!--- I think that the addition to the last sentence here is probably an improvement, but it still doesn't quite address my question -- there's not much of an argument for concluding that dynamic models are *required*. The implicit argument seems to be something like, ''look, there's a lot of complex stuff that's happening here; we can't figure out how to model how the evolutionary trajectories will play out without a dynamic model, so we're just going to assume that it's not possible''. My tendency is to be careful with these kinds of bold claims, and maybe instead emphasise that dynamic models *can be useful* for understanding these kinds of dynamics without suggesting that they are necessary (time will tell if this is true -- I don't want to dissuade someone from giving it a shot -- Corina Tarnita, whose work I've often disagreed with, made a good point about this in a recent comment of Physics of Life Reviews). --->

@@

<!--- Last time we were through this, it was suggested that I scrap the former term ''inbreeding strategy'' because we don't deal at all with inbreeding preference. I have rewritten these sections in attempt to make the writing clearer. TODO: Additionally, I have tweaked the figure legends appropriately. --->

@@

Evolution of reproductive strategies cannot be presumed to occur in isolation in wild populations, and is instead likely to involve multiple interacting phenotypes resulting in the potential for feedback and degeneracy (i.e., functional redundance) among phenotypes under selection. For example, strong inbreeding depression in offspring fitness is widely hypothesised to drive selection for inbreeding avoidance, which could consequently feed back to drive selection for polyandry [e.g., @Zeh1997; @Jennions2000; @Tregenza2002]. Evolution of inbreeding avoidance can be driven by selection on both pre-copulatory and post-copulatory mechanisms, so simultaneous evolution of each phenotype is likely to be defined by degeneracy, in addition to any direct costs on phenotypes. We used individual-based modelling to explore evolution of pre-copulatory and post-copulatory inbreeding avoidance and polyandry given (1) hard constraints on evolution of post-copulatory inbreeding avoidance, (2) asymmetric costs of pre-copulatory and post-copulatory inbreeding avoidance, and (3) evolution of one inbreeding avoidance phenotype given the pre-existence the other. We thereby highlight fundamental but theoretically under-developed relationships between evolution of female mating frequency and pre-copulatory versus post-copulatory inbreeding avoidance.
